---
title: "Assignment 2.1"
subtitle: "CPSC 292 Section 02 -- Hansen"
author: "Hilary Santos"
date: "10/01/2022"
output: html_notebook
---

## Assignment 2.1 

```{r, include=TRUE}
# Loading required libraries

```

### Question 1

*Load the pressure data set. Make a plot of vapor pressure in mmHg versus temperature in C of mercury. Set the axis labels and title. Make the same plot using a different method (either with or without a formula).*

Plot without a formula: 
```{r, include=TRUE}
data("pressure")

plot(pressure$temperature, pressure$pressure, 
     xlab = "Temperature (C)",
     ylab = "Vapor Pressure (mmHg)",
     main= "Vapor Pressure v Temperature on Mercury")
```

Plot with a formula: 
```{r, include=TRUE}
data("pressure")

plot(pressure ~ temperature, data = pressure,
     xlab = "Temperature (C)",
     ylab = "Vapor Pressure (mmHg)",
     main= "Vapor Pressure v Temperature on Mercury")
```


### Question 2

*Load the dataset Loblolly. Make a plot of height versus age of trees where data are triangle-shaped points. Color the points according to the seed number.*

```{r, include=TRUE}
data("Loblolly")
force(Loblolly)

seeds <- c("red", "orange","yellow", "green", "blue", "purple", "orchid4", "black", "gray", "pink", "brown", "tan", "yellowgreen")

plot(Loblolly$age, Loblolly$height,
     xlab = "Age",
     ylab = "Height",
     main = "Loblolly Tree Height v Age",
     pch=2,
     col=seeds[Loblolly$Seed])
```